\chapter*{Conclusion}\addcontentsline{toc}{chapter}{Conclusion}
In this project our topic was scheduling, we decided to focus on \siemens since we had the opportunity to get some insider info and also some of the schedules. 

We started of by researching and writing a problem analysis. In the problem analysis there have been several different aspects that we have taken into account. These include \siemens' employee's needs and rights, existing solutions the union agreements as well as the more abstract term, fairness, among others. All of theses topics have been of great importance when building a solid foundation of knowledge which we could use to make a clear problem definition. With a tangible problem we could move on to the solution phase of the project.

In the second part of our report, which was focused on the development of the program we had to create. It was of utmost importance  to understand the requirements for the program as well as how the program flow should work. Because of the requirements we learned about in the problem analysis and our limited time scope, it was necessary to prioritize the features of our program. The list of priorities proved to be quite useful, since we always knew what to focus on.
It was also important to focus on the structure on the program itself both on an overall level between group members and on a more detailed level for what we had individually written. This helped organize and structure the development of the program.
Lastly, we documented the implementation of the program and the tests, which was quite important for helping the reader and ourselves get an overview of the finished program.

Finally, we can conclude that we have created a well functioning program, that takes the necessary requirements into account and is far more efficient than the current, manual scheduling method at \siemens. The program can easily be improved, but considering the time frame and what we managed to implement from our prioritized requirements list, we feel we have accomplished what we set out to do.
