\chapter*{Introduction}\addcontentsline{toc}{chapter}{Introduction}
In this report we will be documenting the process of our project work. The focus of our project is work scheduling. We will be working with a real-life case from \siemens. Our aim is to figure out how to automate the process of generating the final schedule, and hopefully saving the company time as a result.

Throughout the problem analysis we will be covering topics such as union agreements, fairness, needs of the interested parties, and the already existing solutions. Especially the interested parties are of particular importance, since there are many of them and they each have different levels of influence. Firstly the employees, who have a great interest in topic but have little influence. Therefore it has also been necessary to understand the unions and the union agreements, since they represent the employees. Of course the employers are also important regarding this topic, since they also have a great interest in topic and a lot of power. The analysis of these topics, and in particular the interested parties, will be of great importance when specifying our program requirements since they must be considered when generating a work schedule \siemens can actually use.

As the last part of this report, we will in detail describe how the program itself works. This will be done through a description of the requirements for the program, the specification and design of the program, as well as the overall structure and implementation of our program and the individual parts. 
Our motivation for working with \siemens as our case was that we wanted to work with a real-life case instead of a purely theoretical one.