\section{Working with our supervisor}
The work with our supervisor has been quite beneficial and useful to our group, since he has consistently provided our group with the necessary feedback, needed for our project. This has been done though both emails as well as weekly, virtual meetings on Microsoft Teams.

However, we had one incident where a misunderstanding occurred between our group and our supervisor. It was regarding some programming exercises that our supervisor expected us to complete, but our group wanted to focus on the problem analysis instead. These different expectations were somewhat quickly sorted out in one of our weekly meetings.
What we have learned from that incident was that communication is essential when working with your supervisor, since misunderstandings and different expectations regarding the project can easily occur. Therefore, it is of absolute importance to communicate often and effectively.

As previously mentioned, our group work has been mostly efficient and smooth. Therefore we have also quite quickly worked through the top priorities of our programs, as mentioned in the "Specification and design" section. Therefore our supervisor has been good at pressuring us to accomplish more than we originally set out to do. One of the topics that our supervisor asked us to investigate, was the time complexity of our scheduling algorithm. 
This has proven to be a difficult but rewarding task. In that sense it has been beneficial to us that we had a supervisor who could "pressure" us the right amount. That way we would get the most of our project work.

\section{What to improve in future projects}
In future projects we need to improve our usage of daily goals, as we need to make sure to make them every day, and also use them more effectively as guidelines to what we need to do. We would also like in future projects to be a bit more ambitious about our program and choice of topic, as this program, although a small one, still is very simple and did not need much advanced math or theory to solve. We also need to improve communication with our supervisor, as there has been a few miscommunications between the group and our supervisor. Furthermore, we need to make sure every member of the group knows what to work with, as there has been problems where members did not know what they should begin doing after completing their current task. This consequently meant that some group members did not work on anything while waiting to figure out what to do.

\section{Meta-reflection and conclusion}
So what can we do better in our next project? We need to make sure the first thing we do each day is to set some daily goals, and check if we reached the goal of yesterday. This way we are certain that what should be done today is clear, and it would also mean that everyone knew what to do the specific day. This would hopefully also make sure that everyone had something to work on, and therefore decrease or remove the non-productive time.

Our project work has overall been quite well functioning and effective, but there are a few areas, such as daily goals that we can still improve. It has definitely been interesting to work with a real life case, especially already in P1. It has forced us to take concepts like union agreements and fairness into consideration. We fully believe that this project has helped us learn not only about our very narrow problem delineation but about working with real cases as well.
